DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-18 paper/overview.tex
Add link to videos

Despite these issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we used for training. In our testing, we found 
that the DeepPicar could remain on a fairly challenging track for over 
10 minutes at a moderate speed (50\% throttle), at which point we stopped
the experiment, and more than one minute at a higher speed (75\%
throttle)~\footnote{A collection of self-driving videos can be found
  at: \fixme{Michael: link your video}
  %% \url{https://photos.app.goo.gl/ce93sU7jPk4ywO8u2}
}. Running at
higher speed is inherently more challenging because the CNN controller
has less time to recover from mistakes (bad predictions).  Also, we
find that the prediction accuracy is significantly affected by the
quality of training data as well as various environmental factors such
as lighting conditions. We plan to investigate more systematic ways
to improve the CNN's prediction accuracies.

>>>>

Despite these issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we used for training. In our testing, we found 
that the DeepPicar could remain on a fairly challenging track for over 
10 minutes at a moderate speed (50\% throttle), at which point we stopped
the experiment, and more than one minute at a higher speed (75\%
throttle)~\footnote{A collection of self-driving videos can be found
  at: \url{https://photos.app.goo.gl/q40QFieD5iI9yXU42}
  %% \url{https://photos.app.goo.gl/ce93sU7jPk4ywO8u2}
}. Running at
higher speed is inherently more challenging because the CNN controller
has less time to recover from mistakes (bad predictions).  Also, we
find that the prediction accuracy is significantly affected by the
quality of training data as well as various environmental factors such
as lighting conditions. We plan to investigate more systematic ways
to improve the CNN's prediction accuracies.
